Preliminary (quick and dirty) results

### 2022-10-13 slides/data_checking.Rmd
teeny updates before mariam meeting today

>>>>

## Novel fact recall

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_recall = mean(acc_recall)) %>% 
  left_join(q_google_demos, by = "subj_num") %>% 
  filter(gender %in% c("male", "female")) %>% 
  ggplot(aes(x = j_score, y = acc_recall, color = gender, fill = gender)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = "% correct recall for novel facts") +
  theme_bw()
```

### 2022-10-13 slides/results.Rmd
teeny updates before mariam meeting today

require(xaringanthemer)
source(here::here("R", "get_cleaned_data.R"))
```

@@

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  group_by(subj_num, j_score, resp_pic) %>%
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 3)), fill = fct_rev(cut_number(j_score, 3)))) + 
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_smooth(method = "lm", alpha = 0.2) + 
  scale_x_continuous(breaks = 0:1) +
  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  labs(x = "Photo recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise tertile",
       fill = "Expertise tertile") +
  theme_bw()
```

@@

```{r}
encoding %>% 
  mutate(j_score = j_score - 0.7) %>% 
  lme4::lmer(resp ~ j_score + already_knew + (1 | subj_num), data = .) %>% 
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ j_score + (1 | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         # scaled to units of 0.1
         j_score = (j_score - 0.7) * 10,
         interest = (interest / 100) - .5) %>% 
  lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>%
  # filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source),
                ~if_else(. > 0, 1L, 0L))) %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_pic = mean(resp_pic),
            acc_source = mean(resp_source)) %>% 
  pivot_longer(cols = starts_with("acc"),
               names_to = "memory_type",
               values_to = "acc",
               names_prefix = "acc_") %>% 
  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         # across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         across(c(resp_pic, resp_source), ~(. / 100)),
         interest = (interest / 100) - 0.5,
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + interest + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         j_score = j_score - 0.7) %>% 
  lme4::glmer(acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         # so, like 20% of participants have no retrieval trials where they missed on both source and pic
         # so this is run only using trials where people got _either_ source _or_ pic
         # aka the difference between getting one and getting both
         resp_either = resp_pic + resp_source - 1,
         j_score = j_score - 0.7) %>% 
  filter(resp_either > -1) %>% 
  lme4::glmer(acc_recall ~ resp_either * j_score + (1 + resp_either | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

>>>>

require(xaringanthemer)
source(here::here("R", "get_cleaned_data.R"))

count_streak <- function (acc_col, min_streak_length = 3) {
  streak_count <- 0
  current_streak <- 0
  for (i in 1:length(acc_col)) {
    if (acc_col[i] == 0) current_streak <- 0
    if (acc_col[i] == 1) {
      current_streak <- current_streak + acc_col[i]
      if (current_streak == min_streak_length) {
        # Only triggered once per streak because using == not >=
        streak_count <- streak_count + 1
      }
    }
  }
  return (streak_count)
}
```

@@

```{r}
retrieval %>%
  filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source, acc_recall),
                ~if_else(. > 0, 1L, 0L))) %>% 
  group_by(subj_num, j_score) %>% 
  summarize(acc_pic = mean(resp_pic),
            acc_source = mean(resp_source),
            acc_fact = mean(acc_recall)) %>% 
  pivot_longer(cols = starts_with("acc"),
               names_to = "memory_type",
               values_to = "acc",
               names_prefix = "acc_") %>% 
  ggplot(aes(x = j_score, y = acc, color = memory_type, fill = memory_type)) +
  geom_hline(yintercept = 0.5, linetype = "dotted") +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~ memory_type) +
  guides(color = "none", fill = "none") +
  labs(x = "Expertise score", y = " Mean accuracy WITHOUT confidence (0 to 1)",
       title = "Memory as a function of trivia expertise",
       subtitle = "Only trials with fully novel facts") +
  theme_bw()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         acc_recall = if_else(acc_recall == 0.5, 1, acc_recall)) %>%
  group_by(subj_num, j_score, resp_pic) %>%
  summarize(acc_recall = mean(acc_recall)) %>% 
  ggplot(aes(x = resp_pic, y = acc_recall, color = fct_rev(cut_number(j_score, 2)), fill = fct_rev(cut_number(j_score, 1)))) + 
  geom_line(aes(group = subj_num), alpha = 0.1) +
  geom_smooth(method = "lm", alpha = 0.2) + 
  scale_x_continuous(breaks = 0:1) +
  scale_color_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  scale_fill_viridis_d(begin = 0.2, end = 0.9, direction = -1) +
  labs(x = "Photo recognition accuracy",
       y = "Fact recall accuracy (generous)",
       color = "Expertise median split",
       fill = "Expertise median split") +
  theme_bw()
```
???

Main figure subplots: coefplot, a better version of this with median split and as close to trialwise data as possible, with Bayesian model fit ribbons on top

???

Same plot subfigures as the previous

Also, see about running a model with pic/source as a covariate to explicitly test the difference in interactions

@@

```{r}
encoding %>% 
  mutate(j_score = (j_score - 0.7) * 10) %>% 
  lme4::lmer(resp ~ j_score + already_knew + (1 | subj_num), data = .) %>% 
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         j_score = (j_score - 0.7) * 10) %>% 
  lme4::glmer(acc_recall ~ j_score + (1 | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         # scaled to units of 0.1
         j_score = (j_score - 0.7) * 10,
         # scaled to units of 0.1 where 1 is the full scale
         interest = (interest / 10) - 5) %>% 
  lme4::glmer(acc_recall ~ j_score + interest + (1 + interest | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         # across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         across(c(resp_pic, resp_source), ~(. / 100)),
         interest = (interest / 10) - 5,
         j_score = (j_score - 0.7) * 10) %>% 
  lme4::glmer(acc_recall ~ resp_pic * j_score + interest + (1 + resp_pic | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         j_score = (j_score - 0.7) * 10) %>% 
  lme4::glmer(acc_recall ~ resp_source * j_score + (1 + resp_source | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```

@@

```{r}
retrieval %>% 
  filter(already_knew == "none") %>% 
  mutate(acc_recall = as.numeric(acc_recall > 0),
         across(c(resp_pic, resp_source), ~if_else(. > 0, 1L, 0L)),
         # so, like 20% of participants have no retrieval trials where they missed on both source and pic
         # so this is run only using trials where people got _either_ source _or_ pic
         # aka the difference between getting one and getting both
         resp_either = resp_pic + resp_source - 1,
         j_score = (j_score - 0.7) * 10) %>% 
  filter(resp_either > -1) %>% 
  lme4::glmer(acc_recall ~ resp_either * j_score + (1 + resp_either | subj_num), data = ., family = "binomial") %>%
  broom.mixed::tidy() %>%
  filter(effect == "fixed") %>% 
  select(term:statistic) %>% 
  mutate(across(where(is.numeric), signif, digits = 3)) %>% 
  knitr::kable()
```
